---
title: "data_analysis"
author: "finn krauss"
date: "2025-05-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath(".."))
```

## Load Packages

```{r}
setwd("~/R Studio/NSAS Herring/NSAS-Herring")

library(bcp)
library(changepoint)
library(ggrepel)
library(readxl)
library(ggplot2)
library(tidyverse)
library(FSA)
library(strucchange)
library(MASS)
library(hydroGOF)
library(mgcv)
library(INDperform)
library(dplyr)
library(purrr)
library(progress)
library(segmented)
library(FLCore)
library(gridExtra)
```

## Import data

```{r}
load("data/Herring_LAI.Rdata")

### Load functions from "functions"
source("R/functions.R")

### Split data into components
Herring <- list()
Herring$SHOR <- Herring_LAI[Herring_LAI$component == "Shetland_Orkney",]
Herring$Buchan <- Herring_LAI[Herring_LAI$component == "Buchan",]
Herring$Banks <- Herring_LAI[Herring_LAI$component == "Banks",]
Herring$Downs <- Herring_LAI[Herring_LAI$component == "Downs",]

Herring_LAI <- NULL
```

# Change-points

## Identify change-points

```{r}
### Call function "changepoint_analysis" from functions

### Shetland Orkney
results_cpt <- list()
results_cpt$SHOR <- changepoint_analysis(Herring$SHOR, 
                                          region_name = "Shetland/Orkney",
                                          year_col = "year",
                                          Q = 6,
                                          bcp_threshold = 0.7)
# CPT changepoint indices:  12,   19,   23,   25,   34,   43 
# CPT changepoint years:    1983, 1990, 1994, 1996, 2005, 2014 

# BCP changepoint indices:  12,   19,   23,   31,   34,   43 
# BCP changepoint years:    1983, 1990, 1994, 2002, 2005, 2014 

# Consensus changepoints (± 1 yr, min 5 yr apart): 1983, 1990, 2005, 2014 
# CPT only: 1994, 1996 
# BCP only: 1994, 2002

#---------------------------------------------------------------------

### Buchan
results_cpt$Buchan <- changepoint_analysis(Herring$Buchan, 
                                          region_name = "Buchan",
                                          year_col = "year",
                                          Q = 6,
                                          bcp_threshold = 0.7)
# CPT changepoint indices:  15,   18,   22,   38,   40,   47 
# CPT changepoint years:    1986, 1989, 1993, 2009, 2011, 2018 

## BCP Analysis
# BCP changepoint indices:  18,   21,   23,   39,   46 
# BCP changepoint years:    1989, 1992, 1994, 2010, 2017 

## Consensus Analysis
# Consensus changepoints (± 1 yr, min 5 yr apart): 1989, 2009, 2018 
# CPT only: 1986, 1993, 2011 
# BCP only: 1992, 1994, 2010, 2017

#---------------------------------------------------------------------

### Banks
results_cpt$Banks <- changepoint_analysis(Herring$Banks, 
                                          region_name = "Banks",
                                          year_col = "year",
                                          Q = 6,
                                          bcp_threshold = 0.7)
# CPT changepoint indices:  11,   19,   29,   34,   38,   48 
# CPT changepoint years:    1982, 1990, 2000, 2005, 2009, 2019 

## BCP Analysis
# BCP changepoint indices:  12,   19,   29,   30,   34 
# BCP changepoint years:    1983, 1990, 2000, 2001, 2005 

## Consensus Analysis
# Consensus changepoints (± 1 yr, min 5 yr apart): 1982, 1990, 2000, 2005 
# CPT only: 2009, 2019 
# BCP only: 1983, 2001

#---------------------------------------------------------------------

### Downs
results_cpt$Downs <- changepoint_analysis(Herring$Downs, 
                                          region_name = "Downs",
                                          year_col = "year",
                                          Q = 6,
                                          bcp_threshold = 0.7)
# CPT changepoint indices:  16,   28,   30,   40,   44,   49 
# CPT changepoint years:    1987, 1999, 2001, 2011, 2015, 2020 

## BCP Analysis
# BCP changepoint indices:  30,   40 
# BCP changepoint years:    2001, 2011 

## Consensus Analysis
# Consensus changepoints (± 1 yr, min 5 yr apart): 2001, 2011 
# CPT only: 1987, 1999, 2015, 2020  
```

## Plot change-points

```{r}
### Shetland Orkney
plots_SSB_cpt <- list()
plots_SSB_cpt$SHOR <- plot_SSB_cpt(data = Herring$SHOR, 
              changepoints = results_cpt$SHOR$consensus$changepoint_years,
              component = "Shetland / Orkney", 
              SSB_column = "SSB_component", 
              l_bnd_column = "l_bnd_component", 
              u_bnd_column = "u_bnd_component",
              show_hlines = FALSE)
plots_SSB_cpt$SHOR

#---------------------------------------------------------------------

### Buchan
plots_SSB_cpt$Buchan <- plot_SSB_cpt(data = Herring$Buchan, 
              changepoints = results_cpt$Buchan$consensus$changepoint_years,
              component = "Buchan", 
              SSB_column = "SSB_component", 
              l_bnd_column = "l_bnd_component", 
              u_bnd_column = "u_bnd_component", 
              show_hlines = FALSE)
plots_SSB_cpt$Buchan

#---------------------------------------------------------------------

### Banks
plots_SSB_cpt$Banks <- plot_SSB_cpt(data = Herring$Banks, 
              changepoints = results_cpt$Banks$consensus$changepoint_years,
              component = "Banks", 
              SSB_column = "SSB_component", 
              l_bnd_column = "l_bnd_component", 
              u_bnd_column = "u_bnd_component", 
              show_hlines = FALSE)
plots_SSB_cpt$Banks

#---------------------------------------------------------------------

### Downs
plots_SSB_cpt$Downs <- plot_SSB_cpt(data = Herring$Downs, 
              changepoints = results_cpt$Downs$consensus$changepoint_years,
              component = "Downs", 
              SSB_column = "SSB_component", 
              l_bnd_column = "l_bnd_component", 
              u_bnd_column = "u_bnd_component", 
              show_hlines = FALSE)
plots_SSB_cpt$Downs
```

### Save plots

```{r}
ggsave(filename = file.path("plots/", "SSB_cpt_components.png"),
       plot = grid.arrange(
         plots_SSB_cpt$SHOR + theme(axis.title.x = element_blank(), axis.title.y = element_blank()),
         plots_SSB_cpt$Buchan + theme(axis.title.x = element_blank(), axis.title.y = element_blank()),
         plots_SSB_cpt$Banks + theme(axis.title.x = element_blank(), axis.title.y = element_blank()),
         plots_SSB_cpt$Downs + theme(axis.title.x = element_blank(), axis.title.y = element_blank()),
         ncol = 2,
         bottom = "Year",
         left = "SSB in million t"),
       bg = "white",
       width = 15,
       height = 10,
       dpi = 300)
```

# Hysteresis

## Analysis

```{r}
 # Create time-lag object using specified lag
  data$SSB_lag <- lag(data[[ssb_col]], lag_years)
  
  if (!is.null(dataset_name)) {
    assign(dataset_name, data, envir = parent.frame())}

### Examine for time lag
ccf(Herring$SHOR$SSB_component, Herring$SHOR$F, type = "correlation") # 1 year lag
Herring$SHOR$SSB_lag <- lag(Herring$SHOR$SSB_component, 1)

ccf(Herring$Buchan$SSB_component, Herring$Buchan$F, type = "correlation") # 3 years lag
Herring$Buchan$SSB_lag <- lag(Herring$Buchan$SSB_component, 3)

ccf(Herring$Banks$SSB_component, Herring$Banks$F, type = "correlation") # 5 years lag
Herring$Banks$SSB_lag <- lag(Herring$Banks$SSB_component, 5)

ccf(Herring$Downs$SSB_component, Herring$Downs$F, type = "correlation") # 1 year lag
Herring$Downs$SSB_lag <- lag(Herring$Downs$SSB_component, 1)

#---------------------------------------------------------------------
### Call function "breakpoint_analysis"

### Shetland Orkney
results_brkpt <- list()
results_brkpt$SHOR <- breakpoint_analysis(Herring$SHOR, "SSB_component", "F", "year",
                                               lag_years = 1,
                                               region_name = "Shetland Orkney")

# Optimal number of breaks: 5 
# Best breakpoint F values:
# 0.28 0.29 0.189 0.29 0.22 
# Best breakpoint years:
# 1983, 1990, 1997, 2005, 2015
#---------------------------------------------------------------------

### Buchan
results_brkpt$Buchan <- breakpoint_analysis(Herring$Buchan, "SSB_component", "F", "year", 
                                    lag_years = 3, 
                                    region_name = "Buchan")
# Optimal number of breaks: 3
# Best breakpoint F values:
# 0.29 0.189 0.184 
# Best breakpoint years:
# 1990, 1997, 2012 
#---------------------------------------------------------------------

### Banks
results_brkpt$Banks <- breakpoint_analysis(Herring$Banks, "SSB_component", "F", "year", 
                                    lag_years = 5, 
                                    region_name = "Banks")
# Optimal number of breaks: 2
# Best breakpoint F values:
# 0.39 0.29 
# Best breakpoint years:
# 1988, 2005 
#---------------------------------------------------------------------

### Downs
results_brkpt$Downs <- breakpoint_analysis(Herring$Downs, "SSB_component", "F", "year", 
                                    lag_years = 1, 
                                    region_name = "Downs")
# Optimal number of breaks: 4 
# Best breakpoint F values:
# 0.41 0.171 0.073 0.24 
# Best breakpoint years:
# 1987, 2002, 2009, 2016 
```

## Plotting

```{r}
### Call function plot_hysteresis 
plots_hysteresis <- list()

plots_hysteresis$SHOR <- plot_hysteresis(Herring$SHOR, results_brkpt$SHOR$break_years, "Shetland Orkneys", show_msy_btrigger = FALSE)
plots_hysteresis$SHOR

plots_hysteresis$Buchan <- plot_hysteresis(Herring$Buchan, results_brkpt$Buchan$break_years, "Buchan", show_msy_btrigger = FALSE)
plots_hysteresis$Buchan

plots_hysteresis$Banks <- plot_hysteresis(Herring$Banks, results_brkpt$Banks$break_years, "Banks", show_msy_btrigger = FALSE)
plots_hysteresis$Banks

plots_hysteresis$Downs <- plot_hysteresis(Herring$Downs, results_brkpt$Downs$break_years, "Downs", show_msy_btrigger = FALSE)
plots_hysteresis$Downs
```

### save plot

```{r}
ggsave(filename = file.path("plots/", "hysteresis_components.png"),
       plot = grid.arrange(
         plots_hysteresis$SHOR + theme(axis.title.x = element_blank(), axis.title.y = element_blank()),
         plots_hysteresis$Buchan + theme(axis.title.x = element_blank(), axis.title.y = element_blank()),
         plots_hysteresis$Banks + theme(axis.title.x = element_blank(), axis.title.y = element_blank()),
         plots_hysteresis$Downs + theme(axis.title.x = element_blank(), axis.title.y = element_blank()),
         ncol = 2,
         bottom = "F",
         left = "SSB in million t"),
       bg = "white",
       width = 15,
       height = 10,
       dpi = 300)
```

# SRR Non-Stationary

## Analysis

```{r}
### Load model comparison from model_comp_functions.R 
source("R/model_comp_functions.R")

### Shetland Orkney
#### Compare different models
models_SRR <- list()

models_SRR$SHOR <- run_srr_analysis(
  data_for_srr = Herring$SHOR,
  recruit_col = "Recruitment",
  ssb_col = "SSB_component",
  max_breaks = 5,
  use_bic = TRUE)

print(models_SRR$SHOR$comparison_table)

##### strucchange model shows lowest RMSE and high R_sqrt

### Prep data for LOOCV function
dat_SHOR <- Herring$SHOR %>%
  mutate(R_log = log(Recruitment),
         SSB_log = log(SSB_component)) %>%
  dplyr::select(year, Recruitment, SSB_component, R_log, SSB_log) %>%
  na.omit() %>%
  setNames(c("Year", "R", "SSB", "R_log", "SSB_log")) %>%
  as.data.frame()

### Call function "cross_valid" for performing loocv for all models
rmse_mean_SHOR <- cross_valid(dataset = dat_SHOR)
#         linear    beverton    ricker      segmented   seg.log     segm.glm    strucchange
# TEST:   6032494   5917938     5996407     5906258     5705905     5919392     10051737
# TRAIN:  7193145   7998380     7896592     6659682     6947653     6985389     3945464

#### strucchange show best performance for training data, segmented show balanced results.
#### Classic non segmented models show generally bad performance.

### Call function "srr_breakpoint_analysis" to extract SSR breakpoints
results_SRR <- list()
results_SRR$SHOR <- srr_breakpoint_analysis(Herring$SHOR, "SSB_component", "Recruitment", "year", "Shetland Orkney")

# Optimal number of breaks: 3 
# Best breakpoint SSB values:
# 148853.8, 505309.4, 1201916.7 
# Best breakpoint years:
# 1980, 1987, 2001 

#---------------------------------------------------------------------

### Buchan
#### Compare different models
models_SRR$Buchan <- run_srr_analysis(
  data_for_srr = Herring$Buchan,
  recruit_col = "Recruitment",
  ssb_col = "SSB_component",
  max_breaks = 5,
  use_bic = TRUE)

print(models_SRR$Buchan$comparison_table)

##### segmented shows best RSME with good R_sqrt

#### Prep data for LOOCV function
dat_Buchan <- Herring$Buchan %>%
  mutate(R_log = log(Recruitment),
         SSB_log = log(SSB_component)) %>%
  dplyr::select(year, Recruitment, SSB_component, R_log, SSB_log) %>%
  na.omit() %>%
  setNames(c("Year", "R", "SSB", "R_log", "SSB_log")) %>%
  as.data.frame()

#### Call function "cross_valid" for performing loocv for all models
rmse_mean_Buchan <- cross_valid(dataset = dat_Buchan)

#         linear    beverton    ricker    segmented   seg.log     segm.glm    strucchange
# TEST:   3896841   3509676     3594420   3800680     3380904     4106180     8088465
# TRAIN:  5799156   6165425     6142350   5736075     6092542     5932873     2064443

#### segmented show good balance and best test values, strucchanege shows strong overfitting

#### Call function "srr_breakpoint_analysis" to extract SSR breakpoints
results_SRR$Buchan <- srr_breakpoint_analysis(Herring$Buchan, "SSB_component", "Recruitment", "year", "Buchan", method = "segmented")

# Running segmented model analysis
# Using mean SSB as initial psi: 309942.8 
# Segmented model breakpoint:
# SSB breakpoint: 98449.3 ± 181693.3 
# Approximate year: 1982 

#---------------------------------------------------------------------

### Banks
#### Compare different models
models_SRR$Banks <- run_srr_analysis(
  data_for_srr = Herring$Banks,
  recruit_col = "Recruitment",
  ssb_col = "SSB_component",
  max_breaks = 5,
  use_bic = TRUE)

print(models_SRR$Banks$comparison_table)

##### strucchange model shows lowest RMSE and high R_sqrt

#### Prep data for LOOCV function
dat_Banks <- Herring$Banks %>%
  mutate(R_log = log(Recruitment),
         SSB_log = log(SSB_component)) %>%
  dplyr::select(year, Recruitment, SSB_component, R_log, SSB_log) %>%
  na.omit() %>%
  setNames(c("Year", "R", "SSB", "R_log", "SSB_log")) %>%
  as.data.frame()

#### Call function "cross_valid" for performing loocv for all models
rmse_mean_Banks <- cross_valid(dataset = dat_Banks)

#         linear    beverton    ricker    segmented   seg.log     segm.glm    strucchange
# TEST:   2298870   1970034     1954005   2399083     2038932     2370782     4248983
# TRAIN:  3211518   3180706     3133516   2988736     3112284     3020506     1154869

#### Non segmented models only show onpar test performance with segmented. strucchange overfitting again, segmented outperform for train.

#### Call function "srr_breakpoint_analysis" to extract SSR breakpoints
results_SRR$Banks <- srr_breakpoint_analysis(Herring$Banks, "SSB_component", "Recruitment", "year", "Banks")

# Optimal number of breaks: 3 
# Best breakpoint SSB values:
# 38326.5, 307682.7, 303694 
# Best breakpoint years:
# 1980, 1987, 2001 

#---------------------------------------------------------------------

### Downs
#### Compare different models
models_SRR$Downs <- run_srr_analysis(
  data_for_srr = Herring$Downs,
  recruit_col = "Recruitment",
  ssb_col = "SSB_component",
  max_breaks = 5,
  use_bic = TRUE)

print(models_SRR$Downs$comparison_table)

##### segmented regression model shows lowest RMSE and high R_sqrt

#### Prep data for LOOCV function
dat_Downs <- Herring$Downs %>%
  mutate(R_log = log(Recruitment),
         SSB_log = log(SSB_component)) %>%
  dplyr::select(year, Recruitment, SSB_component, R_log, SSB_log) %>%
  na.omit() %>%
  setNames(c("Year", "R", "SSB", "R_log", "SSB_log")) %>%
  as.data.frame()

#### Call function "cross_valid" for performing loocv for all models
rmse_mean_Downs <- cross_valid(dataset = dat_Downs)

#         linear    beverton    ricker      segmented   seg.log     segm.glm    strucchange
# TEST:   10947162  9919600     15101560    6227837     5940221     5632788     7576975
# TRAIN:  1784159   1771427     1936651     1619286     1688248     1611886     1237352

#### segmented outperform classical models for train data

#### Call function "srr_breakpoint_analysis" to extract SSR breakpoints
results_SRR$Downs <- srr_breakpoint_analysis(Herring$Downs, "SSB_component", "Recruitment", "year", "Downs", method = "segmented")

# Running segmented model analysis
# Using mean SSB as initial psi: 305881.4 
# Segmented model breakpoint:
# SSB breakpoint:   25587.2 ± 3723 
# Approximate year: 1982
```

## Plotting

```{r}
### Call "plot_SRR" function from functions.R
### Shetland Orkney
plots_SRR <- list()
plots_SRR$SHOR <- plot_SRR(Herring$SHOR, break_years = results_SRR$SHOR$break_years,
                          title_stock = "Shetland Orkney", 
                          used_model = "strucchange", 
                          ssb_col = "SSB_component",
                          show_Blim = FALSE,
                          nudge_params = list(
                            list(nudge_y = -8, nudge_x = 0.1),    # first year
                            list(nudge_y = 0, nudge_x = -0.2),    # breakpoint
                            list(nudge_y = -15, nudge_x = 0),     # last year
                            list(nudge_y = -0, nudge_x = 0.2)))   # more breakpoints
plots_SRR$SHOR

#---------------------------------------------------------------------

### Buchan
plots_SRR$Buchan <- plot_SRR(Herring$Buchan, break_years = results_SRR$Buchan$breakpoint_year,
                          title_stock = "Buchan", 
                          used_model = "strucchange", 
                          ssb_col = "SSB_component",
                          show_Blim = FALSE,
                          nudge_params = list(
                            list(nudge_y = -8, nudge_x = 0.1),    # first year
                            list(nudge_y = 0, nudge_x = -0.2),    # breakpoint
                            list(nudge_y = -25, nudge_x = 0),     # last year
                            list(nudge_y = -0, nudge_x = 0.2)))   # more breakpoints
plots_SRR$Buchan

#---------------------------------------------------------------------

### Banks
plots_SRR$Banks <- plot_SRR(Herring$Banks, break_years = results_SRR$Banks$break_years,
                          title_stock = "Banks", 
                          used_model = "strucchange", 
                          ssb_col = "SSB_component",
                          show_Blim = FALSE,
                          nudge_params = list(
                            list(nudge_y = -8, nudge_x = 0.1),    # first year
                            list(nudge_y = 10, nudge_x = -0.1),    # breakpoint
                            list(nudge_y = -25, nudge_x = 0),     # last year
                            list(nudge_y = -0, nudge_x = 0.2)))   # more breakpoints
plots_SRR$Banks

#---------------------------------------------------------------------

### Downs
plots_SRR$Downs <- plot_SRR(Herring$Downs, break_years = results_SRR$Downs$breakpoint_year,
                          title_stock = "Downs", 
                          used_model = "segmented", 
                          ssb_col = "SSB_component",
                          show_Blim = FALSE,
                          nudge_params = list(
                            list(nudge_y = -8, nudge_x = 0.1),    # first year
                            list(nudge_y = 10, nudge_x = -0.1),    # breakpoint
                            list(nudge_y = -25, nudge_x = 0),     # last year
                            list(nudge_y = -0, nudge_x = 0.2)))   # more breakpoints
plots_SRR$Downs
```

#### save plot

```{r}
ggsave(filename = file.path("plots/", "SRR_components.png"),
       plot = grid.arrange(
         plots_SRR$SHOR + theme(axis.title.x = element_blank(), axis.title.y = element_blank()),
         plots_SRR$Buchan + theme(axis.title.x = element_blank(), axis.title.y = element_blank()),
         plots_SRR$Banks + theme(axis.title.x = element_blank(), axis.title.y = element_blank()),
         plots_SRR$Downs + theme(axis.title.x = element_blank(), axis.title.y = element_blank()),
         ncol = 2,
         bottom = "SSB in million t",
         left = "R in billions"),
       bg = "white",
       width = 15,
       height = 10,
       dpi = 300)
```

# tGAM

## Analysis

```{r}
### Load env and cpr data
load("data/env_df_subset.Rdata")
load("data/cpr_component.Rdata")

### Call "run_threshold_analysis" from functions and extract results (below)
#### SHOR
run_threshold_analysis(Herring$SHOR, cpr_component, env_df_subset, "Shetland_Orkney")
#### Buchan
run_threshold_analysis(Herring$Buchan, cpr_component, env_df_subset, "Buchan")
#### Banks
run_threshold_analysis(Herring$Banks, cpr_component, env_df_subset, "Banks")
#### Downs
run_threshold_analysis(Herring$Downs, cpr_component, env_df_subset, "Downs")
```

## Results

#### SHOR

```         
Autumn based analysis
Variable: SST
Time range: 1993 - 2023    LOOCV result: FALSE   Model MR: 11.5437                         Variable: SBT
Time range: 1993 - 2023    LOOCV result: FALSE   Model MR: 9.514                           Variable: SSS
Time range: 1993 - 2023    LOOCV result: TRUE   Model MR: 35.0796                          Variable: Phytoplankton
Time range: 1973 - 2021    LOOCV result: TRUE   Model MR: 25984.45                         Variable: Small zooplankton
Time range: 1973 - 2021    LOOCV result: FALSE   Model MR: 1359.696                        

Lagged autumn based analysis
Variable: SST
Time range: 1994 - 2023    LOOCV result: FALSE   Model MR: 11.2821                         Variable: SBT
Time range: 1994 - 2023    LOOCV result: FALSE   Model MR: 9.5288                          Variable: SSS
Time range: 1994 - 2023    LOOCV result: FALSE   Model MR: 35.0837                         Variable: Phytoplankton
Time range: 1973 - 2022    LOOCV result: TRUE   Model MR: 26598.41                         Variable: Small zooplankton
Time range: 1973 - 2022    LOOCV result: FALSE   Model MR: 1342.1                          

Year based analysis
Variable: SST
Time range: 1993 - 2023    LOOCV result: FALSE   Model MR: 9.692                           Variable: SBT
Time range: 1993 - 2023    LOOCV result: FALSE   Model MR: 7.979                           Variable: SSS
Time range: 1993 - 2023    LOOCV result: FALSE   Model MR: 35.0815                         Variable: Phytoplankton  #### Time range: 1973 - 2021    LOOCV result: FALSE   Model MR: 155865.6                                            ### Variable: Small zooplankton  #### Time range: 1973 - 2021    LOOCV result: TRUE   Model MR: 1297.602                        
```

-   Autumn based: SSS (Model MR: 35.08), Phytoplankton (Model MR: 25984.45)
-   Lagged autumn based: Phytoplankton (Model MR: 26598.41)
-   Year based: Small zooplankton (Model MR: 1297.60)

#### Buchan

```         
Autumn based analysis
Variable: SST
Time range: 1993 - 2023    LOOCV result: FALSE   Model MR: 11.6811                         Variable: SBT
Time range: 1993 - 2023    LOOCV result: FALSE   Model MR: 10.1628                         Variable: SSS
Time range: 1993 - 2023    LOOCV result: FALSE   Model MR: 34.7647                         Variable: Phytoplankton
Time range: 1975 - 2021    LOOCV result: TRUE   Model MR: 67855.51                         Variable: Small zooplankton
Time range: 1975 - 2021    LOOCV result: TRUE   Model MR: 507.1388                         

Lagged autumn based analysis
Variable: SST
Time range: 1994 - 2023    LOOCV result: FALSE   Model MR: 11.6994                         Variable: SBT
Time range: 1994 - 2023    LOOCV result: TRUE   Model MR: 9.9864                           Variable: SSS
Time range: 1994 - 2023    LOOCV result: FALSE   Model MR: 34.7634                         Variable: Phytoplankton
Time range: 1975 - 2022    LOOCV result: FALSE   Model MR: 67500.27                        Variable: Small zooplankton
Time range: 1975 - 2022    LOOCV result: TRUE   Model MR: 504.4396                         

Year based analysis
Variable: SST
Time range: 1993 - 2023    LOOCV result: FALSE   Model MR: 10.131                          Variable: SBT
Time range: 1993 - 2023    LOOCV result: FALSE   Model MR: 8.2791                          Variable: SSS
Time range: 1993 - 2023    LOOCV result: TRUE   Model MR: 34.7789                          Variable: Phytoplankton
Time range: 1975 - 2021    LOOCV result: FALSE   Model MR: 121993.8                        Variable: Small zooplankton
Time range: 1975 - 2021    LOOCV result: TRUE   Model MR: 837.6338                         
```

-   Autumn based: Phytoplankton (67855.51), Small zooplankton (507.14)
-   Lagged autumn based: SBT (9.99), Small zooplankton (504.44)
-   Year based: SSS (34.78), Small zooplankton (837.63)

#### Banks

```         
Autumn based analysis
Variable: SST
Time range: 1993 - 2023    LOOCV result: FALSE   Model MR: 12.2594                         Variable: SBT
Time range: 1993 - 2023    LOOCV result: FALSE   Model MR: 11.8582                         Variable: SSS
Time range: 1993 - 2023    LOOCV result: FALSE   Model MR: 34.4194                         Variable: Phytoplankton
Time range: 1977 - 2021    LOOCV result: FALSE   Model MR: 48561.05                        Variable: Small zooplankton
Time range: 1977 - 2021    LOOCV result: FALSE   Model MR: 722.24                          

Lagged autumn based analysis
Variable: SST
Time range: 1994 - 2023    LOOCV result: FALSE   Model MR: 12.2892                         Variable: SBT
Time range: 1994 - 2023    LOOCV result: FALSE   Model MR: 11.3731                         Variable: SSS
Time range: 1994 - 2023    LOOCV result: FALSE   Model MR: 34.4255                         Variable: Phytoplankton
Time range: 1977 - 2022    LOOCV result: TRUE   Model MR: 81503.98                         Variable: Small zooplankton
Time range: 1977 - 2022    LOOCV result: FALSE   Model MR: 562.6765                        

Year based analysis
Variable: SST
Time range: 1993 - 2023    LOOCV result: FALSE   Model MR: 10.2462                         Variable: SBT
Time range: 1993 - 2023    LOOCV result: FALSE   Model MR: 9.5233                          Variable: SSS
Time range: 1993 - 2023    LOOCV result: FALSE   Model MR: 34.4321                         Variable: Phytoplankton
Time range: 1977 - 2021    LOOCV result: FALSE   Model MR: 54101.01                        Variable: Small zooplankton
Time range: 1977 - 2021    LOOCV result: FALSE   Model MR: 788.027
```

-   Lagged autumn based: Phytoplankton (Model MR: 81503.98)

#### Downs

```         
Autumn based analysis
Variable: SST
Time range: 1993 - 2023    LOOCV result: FALSE   Model MR: 15.2948                         Variable: SBT
Time range: 1993 - 2023    LOOCV result: FALSE   Model MR: 15.309                          Variable: SSS
Time range: 1993 - 2023    LOOCV result: FALSE   Model MR: 34.3209                         Variable: Phytoplankton
Time range: 1973 - 2020    LOOCV result: FALSE   Model MR: 24908.67                        Variable: Small zooplankton
Time range: 1973 - 2020    LOOCV result: FALSE   Model MR: 297.6947                        

Lagged autumn based analysis
Variable: SST
Time range: 1994 - 2023    LOOCV result: FALSE   Model MR: 15.2864                         Variable: SBT
Time range: 1994 - 2023    LOOCV result: FALSE   Model MR: 15.2964                         Variable: SSS
Time range: 1994 - 2023    LOOCV result: FALSE   Model MR: 34.4379                         Variable: Phytoplankton
Time range: 1973 - 2021    LOOCV result: FALSE   Model MR: 24847.2                         Variable: Small zooplankton
Time range: 1973 - 2021    LOOCV result: FALSE   Model MR: 689.1399                        

Year based analysis
Variable: SST
Time range: 1993 - 2023    LOOCV result: FALSE   Model MR: 12.2222                         Variable: SBT
Time range: 1993 - 2023    LOOCV result: FALSE   Model MR: 12.2065                         Variable: SSS
Time range: 1993 - 2023    LOOCV result: FALSE   Model MR: 34.3582                         Variable: Phytoplankton
Time range: 1973 - 2021    LOOCV result: FALSE   Model MR: 46859.85                        Variable: Small zooplankton
Time range: 1973 - 2021    LOOCV result: FALSE   Model MR: 699.3112                        
```

-   No significant thresholds found.
